Constructing the transition graphs of interacting hysterons

### 2022-06-23 Paper_draft.tex

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{xcolor}
\newcommand\note[1]{\textcolor{red}{#1}}
\usepackage{amsmath}
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

@@

It often occurs that one or more of the possible states for $N$ hysterons cannot be reached from the ground state. As is customary, we refer to states that cannot be reached as garden-of-Eden states. Because the transitions from garden-of-Eden states are irrelevant when one starts from the ground state, as is generally the case in our experiments, we may choose to ignore garden-of-Eden states. As a consequence, when two graphs only differ from one another by transitions that occur from garden-of-Eden states, the graphs become duplicates. Therefore, when garden-of-Eden states are ignored, the number of distinct graphs can turn out lower than the number of possible combinations of transitions. For $N=2$, ignoring garden-of-Eden states  reduces the number of graphs from 1458 to 752. 

@@

>>>>

\usepackage[pdftex]{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage[table]{xcolor}
\newcommand\note[1]{\textcolor{red}{#1}}
\usepackage{amsmath}
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

@@

\newcommand\x{0.11\textwidth}

@@

It often occurs that one or more of the possible states for $N$ hysterons cannot be reached from the ground state. As is customary\cite{juleslechenault2021}, we refer to states that cannot be reached as garden-of-Eden states. Because the transitions from garden-of-Eden states are irrelevant when one starts from the ground state, as is generally the case in our experiments, we may choose to ignore garden-of-Eden states. As a consequence, when two graphs only differ from one another by transitions that occur from garden-of-Eden states, the graphs become duplicates. Therefore, when garden-of-Eden states are ignored, the number of distinct graphs can turn out lower than the number of possible combinations of transitions. For $N=2$, ignoring garden-of-Eden states  reduces the number of graphs from 1458 to 752. 

@@

\begin{table*}[]
\begin{tabular}{|c|c|ccc|c|c|cc|}
\hline
\textbf{(1, 2, 3)} & \textbf{(1, 3, 2)} & \textbf{(2, 3, 1)}&&& \textbf{(2, 1, 3)} & \textbf{(3, 1, 2)} & \textbf{(3, 1, 2)}&\\ \hline
  \includegraphics[width=\x]{21-06-2022_N3graphs_preisach/graph0.pdf}
&\includegraphics[width=\x]{21-06-2022_N3graphs_preisach/graph3.pdf}              
&\includegraphics[width=\x]{21-06-2022_N3graphs_preisach/graph2.pdf}&&                            
&\includegraphics[width=\x]{21-06-2022_N3graphs_preisach/graph1.pdf}                                  
&\includegraphics[width=\x]{21-06-2022_N3graphs_preisach/graph4.pdf}                                  
&\includegraphics[width=\x]{21-06-2022_N3graphs_preisach/graph5.pdf}& \\ \hline             
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph3.pdf}                  
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph11.pdf}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_unsolvable/graph1.pdf}\cellcolor{gray!30}   &   \includegraphics[width=\x]{21-06-2022_N3graphs_base_unsolvable/graph2.pdf}\cellcolor{gray!30}                    
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph5.pdf}                   
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph0.pdf}                      
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph1.pdf}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph12.pdf}\\ 
& \includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph4.pdf}                
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph13.pdf}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_unsolvable/graph2.pdf}\cellcolor{gray!30}   & \includegraphics[width=\x]{21-06-2022_N3graphs_base_unsolvable/graph7.pdf}\cellcolor{gray!30}                
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph9.pdf}                     
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph6.pdf}                   
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph2.pdf}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph14.pdf}\\
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph8.pdf}                  
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph19.pdf}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_unsolvable/graph5.pdf}\cellcolor{gray!30}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_unsolvable/graph6.pdf}\cellcolor{gray!30}               
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph16.pdf}    
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph15.pdf}                         
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph7.pdf}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph17.pdf}\\
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_unsolvable/graph4.pdf}\cellcolor{gray!30}          
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph20.pdf}&&                    
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_unsolvable/graph0.pdf}\cellcolor{gray!30}                    
&                    
&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph10.pdf}&\includegraphics[width=\x]{21-06-2022_N3graphs_base_scrambled/graph18.pdf}\\ \hline

\end{tabular}
\end{table*}
